Hector Permafrost

### 2018-12-19 README.Rmd
Replace `_` with `.` in package name to make it valid

You can install the development version of `hector_permafrost_emit` from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("ashiklom/hector_permafrost_emit")
```

>>>>

You can install the development version of `hector.permafrost.emit` from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("ashiklom/hector.permafrost.emit")
```

### 2018-12-19 analysis/paper/paper.Rmd
Replace `_` with `.` in package name to make it valid

library(hector_permafrost_emit) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

>>>>

library(hector.permafrost.emit) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```
